Automatic Differentiation to Accelerate Inference for Partially Observed Stochastic Processes

### 2023-10-31 mop/draft.tex
Updates from Overleaf

\input{paper/macros}

@@

@@

However, the above algorithm requires access to likelihood ratios, and is therefore not a simulation-based inference method.

>>>>

\input{../paper/macros}

@@

\begin{prop}[Correctness of DOP-$\alpha$ (Algorithm \ref{alg:dop})]
    When $\theta$ is evaluated at $\phi$, 
\end{prop}

@@

However, the above algorithm requires access to likelihood ratios, and is therefore not compatible with simulation-based inference.
